### 2014-04-04 paper/exampleobjects.tex
figure is back

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=7in]{figures/examples.png}
\caption{A series of example objects created using our system.  A) shows a portable radio.  B) shows a presence-aware pen holder.  C) is a rabbit which ``breathes'' using wind pipes we built.  D) shows a maze game we created.  E) is a touch-sensitive brain toy.  \valkyrie{finalize order of example objects.  what order is best?}}
\label{fig:examples}
\end{figure*}

@@

The models we used for the toys' exteriors were all downloaded from the free website Thingiverse.  All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing/?ALLSTEPS}

@@

A custom radio, built using pipes integrated with traditional electronics, allows users to tune to different stations and listen in.  This device uses a network of disconnected open tubes threaded with wires to connect our components (two potentiometers, an LED, and a speaker) to a microcontroller (Arduino Pro Micro).  We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  For the radio functionality, we attached an Si4703 radio tuner breakout board to the Arduino, which offers headphone-jack output.  We fabricated the radio itself on our Makerbot, support-free but cut in two pieces to allow the Arduino and battery pack to be inserted.

@@

\subsection{Animated Neon Sign (semi-closed, threadable, interior)}

@@

\subsection{Maze (fully enclosed, particulate, tree, interior)}

>>>>

\begin{figure*}
\centering
    \includegraphics[width=7in]{figures/examples.png}
\caption{A series of example objects created using our system.  A) shows a portable radio.  B) shows a presence-aware pen holder.  C) is a rabbit which ``breathes'' using wind pipes we built.  D) shows a maze game we created.  E) is a touch-sensitive brain toy.  \valkyrie{finalize order of example objects.  what order is best?}}
\label{fig:examples}
\end{figure*}

@@

@@

The models we used for the toys' exteriors were all downloaded from the free website Thingiverse.  All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing/?ALLSTEPS}.

@@

A custom radio, built using pipes integrated with traditional electronics, allows users to tune to different stations and listen in.  This device uses a network of disconnected open pipes threaded with wires to connect our components (two potentiometers, an LED, and a speaker) to a microcontroller (Arduino Pro Micro). We hid the microcontroller and a battery-driven power supply in the base of the radio to make it portable.  For the radio functionality, we attached an Si4703 radio tuner breakout board to the Arduino, which offers headphone-jack output.

In order to create so many pipes (3 per potentiometer, 1 for the LED, 1 for the speaker) and still preserve surface quality after voxelizing, we added a "High Quality" for pipe-cutting.  This mode voxelizes at a resolution of 512x512x512 instead of our previous 128x128x128.  It does preserve surface geometry, however it requires around 3 minutes to complete a single cut operation, compared to our nearly-instant smaller voxel grid (computation on a 3D grid increases by the cube of the 1D size increase).  We fabricated the radio itself on our Makerbot, support-free but cut in two pieces to allow the Arduino and battery pack to be inserted.

@@

\subsection{Animated Neon Sign (return, threadable, interior)}

@@

\subsection{Maze (fully enclosed, particulate, tree, interior + exterior)}
